### 2020-08-06 data/draft-publications.tex
clean generation

\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.

@@

\subsection{Books and book chapters}

@@

\item Gupta, Subhojoy, \emph{Monodromy groups of CP^1-structures on punctured surfaces}, preprint, \url{https://arxiv.org/abs/1909.10771}.

@@

nonlocal boundary jumps}, J. Phys. A} {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.

@@

Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal.} {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.

@@

rough domains}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.

@@

smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.

@@

general branched structure}, Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.

@@

homogenization of an associated control problem}, Appl. Anal.} {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.

@@

four-sphere}, Math. Ann.} {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.

@@

subset of all {F}ourier coefficients}, Publ. Mat.} {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.

@@

{S}aito-{K}urokawa lifts}, J. Number Theory} {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.

@@

coloring}, J. Algebra} {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.

@@

partitions}, J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.

@@

Linusson, Svante and Nunzi, Fran\c{c}ois, {\em Bumping sequences and multispecies juggling}, Adv. in Appl. Math.} {\bf 98} (2018), 100--126, DOI 10.1016/j.aam.2018.03.001, \url{https://doi.org/10.1016/j.aam.2018.03.001}.

@@

asymmetric exclusion process}, Phys. Rev. E} {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.

@@

exclusion process}, J. Stat. Phys.} {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
\item Ayyer, Arvind and Linusson, Svante, {\em Reverse juggling processes}, Random Structures Algorithms} {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, {\em Odd partitions in {Y}oung's lattice}, S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
\item Ayyer, Arvind and Ramassamy, Sanjay, {\em The {H}ilbert-{G}alton board}, ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774, DOI 10.30757/alea.v15-28, \url{https://doi.org/10.30757/alea.v15-28}.

@@

modular forms}, J. Reine Angew. Math.} {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.

@@

forms and applications}, Adv. Math.} {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.

@@

multipliers on the {H}eisenberg group}, J. Anal. Math.} {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
\item Baklouti, Ali and Thangavelu, Sundaram, {\em Hardy and {M}iyachi theorems for {H}eisenberg motion groups}, Nagoya Math. J.} {\bf 229} (2018), 1--20, DOI 10.1017/nmj.2016.58, \url{https://doi.org/10.1017/nmj.2016.58}.

@@

Verma, Kaushal, {\em Remarks on the higher dimensional {S}uita conjecture}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411, DOI 10.1090/proc/14421, \url{https://doi.org/10.1090/proc/14421}.

@@

operator}, Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25, DOI 10.1007/s12044-019-0471-2, \url{https://doi.org/10.1007/s12044-019-0471-2}.
\item Balodi, Mamta and Palcoux, Sebastien, {\em On {B}oolean intervals of finite groups}, J. Combin. Theory Ser. A} {\bf 157} (2018), 49--69, DOI 10.1016/j.jcta.2018.02.004, \url{https://doi.org/10.1016/j.jcta.2018.02.004}.
\item Banerjee, Abhishek, {\em On {A}uslander's formula and cohereditary torsion pairs}, Commun. Contemp. Math.} {\bf 20} (2018), 1750071, 27, DOI 10.1142/S0219199717500717, \url{https://doi.org/10.1142/S0219199717500717}.
\item Banerjee, Abhishek, {\em Modular {H}ecke algebras over {M}\"{o}bius categories}, J. Geom. Phys.} {\bf 131} (2018), 23--40, DOI 10.1016/j.geomphys.2018.04.008, \url{https://doi.org/10.1016/j.geomphys.2018.04.008}.

@@

objects}, Canad. Math. Bull.} {\bf 62} (2019), 703--714, DOI 10.4153/s0008439518000656, \url{https://doi.org/10.4153/s0008439518000656}.

@@

categories}, C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375, DOI 10.1016/j.crma.2018.02.012, \url{https://doi.org/10.1016/j.crma.2018.02.012}.
\item Banerjee, Abhishek, {\em Quasimodular {H}ecke algebras and {H}opf actions}, J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080, DOI 10.4171/JNCG/297, \url{https://doi.org/10.4171/JNCG/297}.
\item Banerjee, Abhishek, {\em Completions of monoid objects and descent results}, J. Algebra} {\bf 507} (2018), 362--399, DOI 10.1016/j.jalgebra.2018.04.022, \url{https://doi.org/10.1016/j.jalgebra.2018.04.022}.

@@

derivations}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1781--1802, DOI 10.1007/s10231-019-00844-x, \url{https://doi.org/10.1007/s10231-019-00844-x}.

@@

state space}, Math. Oper. Res.} {\bf 43} (2018), 516--532, DOI 10.1287/moor.2017.0870, \url{https://doi.org/10.1287/moor.2017.0870}.

@@

and Putinar, Mihai, {\em Simultaneous kernels of matrix {H}adamard powers}, Linear Algebra Appl.} {\bf 576} (2019), 142--157, DOI 10.1016/j.laa.2018.03.035, \url{https://doi.org/10.1016/j.laa.2018.03.035}.

@@

Morales, Alejandro H. and Yip, Martha, {\em The volume of the caracol polytope}, S\'{e}m. Lothar. Combin.} {\bf 80B} (2018), Art. 87, 12.

@@

Morales, Alejandro H. and Yip, Martha, {\em A combinatorial model for computing volumes of flow polytopes}, Trans. Amer. Math. Soc.} {\bf 372} (2019), 3369--3404, DOI 10.1090/tran/7743, \url{https://doi.org/10.1090/tran/7743}.
\item Bera, Sayani and Verma, Kaushal, {\em Some aspects of shift-like automorphisms of {$\Bbb C^k$}}, Proc. Indian Acad. Sci. Math. Sci.} {\bf 128} (2018), Art. 10, 48, DOI 10.1007/s12044-018-0388-1, \url{https://doi.org/10.1007/s12044-018-0388-1}.

@@

{R}iemann surface}, Doc. Math.} {\bf 23} (2018), 1291--1311.

@@

sufficient kernels}, Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093, DOI 10.1007/s11785-017-0701-5, \url{https://doi.org/10.1007/s11785-017-0701-5}.

@@

selected areas of functional analysis and operator theory}, Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617, DOI 10.1007/s13226-019-0345-4, \url{https://doi.org/10.1007/s13226-019-0345-4}.

@@

interpolation and extension}, J. Funct. Anal.} {\bf 274} (2018), 504--524, DOI 10.1016/j.jfa.2017.09.013, \url{https://doi.org/10.1016/j.jfa.2017.09.013}.

@@

developing countries} {\bf 275} (2019), 42--64.
\item Bhosle, Usha N., {\em Hitchin pairs on reducible curves}, Internat. J. Math.} {\bf 29} (2018), 1850015, 49, DOI 10.1142/S0129167X18500155, \url{https://doi.org/10.1142/S0129167X18500155}.

@@

Pingali, Vamsi P., {\em Rational cuspidal curves on del-{P}ezzo surfaces}, J. Singul.} {\bf 17} (2018), 91--107.

@@

logarithmic connections}, Doc. Math.} {\bf 24} (2019), 2299--2337.

@@

astheno-{K}\"{a}hler manifolds}, \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art. 6, 13.

@@

{FEM} for the {O}seen problem}, Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214, DOI 10.1515/cmam-2018-0020, \url{https://doi.org/10.1515/cmam-2018-0020}.

@@

{${S}_n$}-invariant kernels}, J. Funct. Anal.} {\bf 276} (2019), 751--784, DOI 10.1016/j.jfa.2018.10.025, \url{https://doi.org/10.1016/j.jfa.2018.10.025}.

@@

for some fractional {L}aplacians}, Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605, DOI 10.3934/cpaa.2019116, \url{https://doi.org/10.3934/cpaa.2019116}.
\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal, {\em Comments on the {G}reen's function of a planar domain}, Anal. Math. Phys.} {\bf 8} (2018), 383--414, DOI 10.1007/s13324-017-0177-5, \url{https://doi.org/10.1007/s13324-017-0177-5}.

@@

constraints}, ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206, DOI 10.1051/cocv/2017031, \url{https://doi.org/10.1051/cocv/2017031}.

@@

of manifolds}, Exp. Math.} {\bf 27} (2018), 22--36, DOI 10.1080/10586458.2016.1212747, \url{https://doi.org/10.1080/10586458.2016.1212747}.

@@

indefinite second-order linear elliptic problems}, Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250, DOI 10.1515/cmam-2019-0034, \url{https://doi.org/10.1515/cmam-2019-0034}.

@@

the polydisc}, Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352, DOI 10.1080/17476933.2017.1370461, \url{https://doi.org/10.1080/17476933.2017.1370461}.

@@

difference equation}, Discrete Contin. Dyn. Syst.} {\bf 38} (2018), 1707--1718, DOI 10.3934/dcds.2018070, \url{https://doi.org/10.3934/dcds.2018070}.

@@

semipositive matrices}, Electron. J. Linear Algebra} {\bf 34} (2018), 687--694, DOI 10.13001/1081-3810.3864, \url{https://doi.org/10.13001/1081-3810.3864}.

@@

{D}unkl-{H}ermite operator}, Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544, DOI 10.1017/s0013091517000311, \url{https://doi.org/10.1017/s0013091517000311}.

@@

{K}lingen type {E}isenstein series and applications}, Abh. Math. Semin. Univ. Hambg.} {\bf 89} (2019), 105--116, DOI 10.1007/s12188-019-00206-7, \url{https://doi.org/10.1007/s12188-019-00206-7}.
\item Das, Soumya and Khan, Rizwanur, {\em The third moment of symmetric square {$L$}-functions}, Q. J. Math.} {\bf 69} (2018), 1063--1087, DOI 10.1093/qmath/hay012, \url{https://doi.org/10.1093/qmath/hay012}.

@@

2 in prime powers}, Acta Arith.} {\bf 183} (2018), 167--172, DOI 10.4064/aa170419-4-11, \url{https://doi.org/10.4064/aa170419-4-11}.
\item Das, Soumya and Pal, Ritwik, {\em The first negative eigenvalue of {Y}oshida lifts}, Res. Number Theory} {\bf 5} (2019), Paper No. 20, 9, DOI 10.1007/s40993-019-0158-x, \url{https://doi.org/10.1007/s40993-019-0158-x}.

@@

{A}rchimedean}, Discrete Math.} {\bf 341} (2018), 3296--3309, DOI 10.1016/j.disc.2018.08.016, \url{https://doi.org/10.1016/j.disc.2018.08.016}.

@@

for convection-diffusion-reaction problems}, Numer. Methods Partial Differential Equations} {\bf 35} (2019), 638--663, DOI 10.1002/num.22317, \url{https://doi.org/10.1002/num.22317}.

@@

the optimal control problems governed by {S}tokes equation}, Numer. Funct. Anal. Optim.} {\bf 40} (2019), 421--460, DOI 10.1080/01630563.2018.1538158, \url{https://doi.org/10.1080/01630563.2018.1538158}.
\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P. and Silberman, Lior and Tao, Terence, {\em Homogeneous length functions on groups}, Algebra Number Theory} {\bf 12} (2018), 1773--1786, DOI 10.2140/ant.2018.12.1773, \url{https://doi.org/10.2140/ant.2018.12.1773}.

@@

posteriori} error control of the obstacle problem}, Comput. Math. Appl.} {\bf 75} (2018), 2311--2327, DOI 10.1016/j.camwa.2017.12.010, \url{https://doi.org/10.1016/j.camwa.2017.12.010}.

@@

3{D}-elliptic obstacle problem}, Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236, DOI 10.1515/cmam-2017-0018, \url{https://doi.org/10.1515/cmam-2017-0018}.
\item Garani, Shayan Srinivasa and Seshadri, Harish, {\em An algorithmic approach to {S}outh {I}ndian classical music}, J. Math. Music} {\bf 13} (2019), 107--134, DOI 10.1080/17459737.2019.1604845, \url{https://doi.org/10.1080/17459737.2019.1604845}.
\item Gaussier, Herv\'{e} and Seshadri, Harish, {\em Holomorphic motions and complex geometry}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313, DOI 10.1090/proc/14217, \url{https://doi.org/10.1090/proc/14217}.

@@

C^n$}}, Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641, DOI 10.1007/s40315-018-0243-5, \url{https://doi.org/10.1007/s40315-018-0243-5}.
\item Ghara, Soumitra and Kumar, Surjit, {\em On the sum of two subnormal kernels}, J. Math. Anal. Appl.} {\bf 469} (2019), 1015--1027, DOI 10.1016/j.jmaa.2018.09.048, \url{https://doi.org/10.1016/j.jmaa.2018.09.048}.

@@

diffusions}, Stoch. Anal. Appl.} {\bf 36} (2018), 1--27, DOI 10.1080/07362994.2017.1356732, \url{https://doi.org/10.1080/07362994.2017.1356732}.

@@

obstacle problem}, J. Comput. Appl. Math.} {\bf 357} (2019), 85--102, DOI 10.1016/j.cam.2019.02.026, \url{https://doi.org/10.1016/j.cam.2019.02.026}.

@@

solving parabolic obstacle problem}, Comput. Math. Appl.} {\bf 78} (2019), 3896--3915, DOI 10.1016/j.camwa.2019.06.022, \url{https://doi.org/10.1016/j.camwa.2019.06.022}.

@@

multishifts}, Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608, DOI 10.1090/proc/14410, \url{https://doi.org/10.1090/proc/14410}.

>>>>

\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906\_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.

@@

\subsection{Books}

\subsection{Book Chapters}

\begin{enumerate}
\item Gupta, Subhojoy and Seshadri, Harish, \emph{Complex geometry of Teichmüller domains} in Papadopoulos, Athanase (ed.) (ed.), {\em Handbook of Teichmüller theory} , IRMA Lect. Math. Theor. Phys , Eur. Math. Soc., Zürich (2020), 26.
\item Gupta, Subhojoy, \emph{Holomorphic quadratic differentials in Teichmüller theory} in Papadopoulos, Athanase (ed.) (ed.), {\em Handbook of Teichmüller theory} , IRMA Lect. Math. Theor. Phys. , Eur. Math. Soc., Zürich (2020), 36.
\end{enumerate}

@@

\item Gupta, Subhojoy, \emph{Monodromy groups of $CP^1$-structures on punctured surfaces}, preprint, \url{https://arxiv.org/abs/1909.10771}.

@@

nonlocal boundary jumps}, J. Phys. A {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.

@@

Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal. {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.

@@

rough domains}, Ann. Mat. Pura Appl. (4) {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.

@@

smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.

@@

general branched structure}, Math. Methods Appl. Sci. {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.

@@

homogenization of an associated control problem}, Appl. Anal. {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.

@@

four-sphere}, Math. Ann. {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.

@@

subset of all {F}ourier coefficients}, Publ. Mat. {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.

@@

{S}aito-{K}urokawa lifts}, J. Number Theory {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.

@@

coloring}, J. Algebra {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.

@@

partitions}, J. Combin. Theory Ser. A {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.

@@

Linusson, Svante and Nunzi, Fran\c{c}ois, {\em Bumping sequences and multispecies juggling}, Adv. in Appl. Math. {\bf 98} (2018), 100--126, DOI 10.1016/j.aam.2018.03.001, \url{https://doi.org/10.1016/j.aam.2018.03.001}.

@@

asymmetric exclusion process}, Phys. Rev. E {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.

@@

exclusion process}, J. Stat. Phys. {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
\item Ayyer, Arvind and Linusson, Svante, {\em Reverse juggling processes}, Random Structures Algorithms {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, {\em Odd partitions in {Y}oung's lattice}, S\'{e}m. Lothar. Combin. {\bf 75} (2018), Art. B75g, 13.
\item Ayyer, Arvind and Ramassamy, Sanjay, {\em The {H}ilbert-{G}alton board}, ALEA Lat. Am. J. Probab. Math. Stat. {\bf 15} (2018), 755--774, DOI 10.30757/alea.v15-28, \url{https://doi.org/10.30757/alea.v15-28}.

@@

modular forms}, J. Reine Angew. Math. {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.

@@

forms and applications}, Adv. Math. {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.

@@

multipliers on the {H}eisenberg group}, J. Anal. Math. {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
\item Baklouti, Ali and Thangavelu, Sundaram, {\em Hardy and {M}iyachi theorems for {H}eisenberg motion groups}, Nagoya Math. J. {\bf 229} (2018), 1--20, DOI 10.1017/nmj.2016.58, \url{https://doi.org/10.1017/nmj.2016.58}.

@@

Verma, Kaushal, {\em Remarks on the higher dimensional {S}uita conjecture}, Proc. Amer. Math. Soc. {\bf 147} (2019), 3401--3411, DOI 10.1090/proc/14421, \url{https://doi.org/10.1090/proc/14421}.

@@

operator}, Proc. Indian Acad. Sci. Math. Sci. {\bf 129} (2019), Art. 33, 25, DOI 10.1007/s12044-019-0471-2, \url{https://doi.org/10.1007/s12044-019-0471-2}.
\item Balodi, Mamta and Palcoux, Sebastien, {\em On {B}oolean intervals of finite groups}, J. Combin. Theory Ser. A {\bf 157} (2018), 49--69, DOI 10.1016/j.jcta.2018.02.004, \url{https://doi.org/10.1016/j.jcta.2018.02.004}.
\item Banerjee, Abhishek, {\em On {A}uslander's formula and cohereditary torsion pairs}, Commun. Contemp. Math. {\bf 20} (2018), 1750071, 27, DOI 10.1142/S0219199717500717, \url{https://doi.org/10.1142/S0219199717500717}.
\item Banerjee, Abhishek, {\em Modular {H}ecke algebras over {M}\"{o}bius categories}, J. Geom. Phys. {\bf 131} (2018), 23--40, DOI 10.1016/j.geomphys.2018.04.008, \url{https://doi.org/10.1016/j.geomphys.2018.04.008}.

@@

objects}, Canad. Math. Bull. {\bf 62} (2019), 703--714, DOI 10.4153/s0008439518000656, \url{https://doi.org/10.4153/s0008439518000656}.

@@

categories}, C. R. Math. Acad. Sci. Paris {\bf 356} (2018), 365--375, DOI 10.1016/j.crma.2018.02.012, \url{https://doi.org/10.1016/j.crma.2018.02.012}.
\item Banerjee, Abhishek, {\em Quasimodular {H}ecke algebras and {H}opf actions}, J. Noncommut. Geom. {\bf 12} (2018), 1041--1080, DOI 10.4171/JNCG/297, \url{https://doi.org/10.4171/JNCG/297}.
\item Banerjee, Abhishek, {\em Completions of monoid objects and descent results}, J. Algebra {\bf 507} (2018), 362--399, DOI 10.1016/j.jalgebra.2018.04.022, \url{https://doi.org/10.1016/j.jalgebra.2018.04.022}.

@@

derivations}, Ann. Mat. Pura Appl. (4) {\bf 198} (2019), 1781--1802, DOI 10.1007/s10231-019-00844-x, \url{https://doi.org/10.1007/s10231-019-00844-x}.

@@

state space}, Math. Oper. Res. {\bf 43} (2018), 516--532, DOI 10.1287/moor.2017.0870, \url{https://doi.org/10.1287/moor.2017.0870}.

@@

and Putinar, Mihai, {\em Simultaneous kernels of matrix {H}adamard powers}, Linear Algebra Appl. {\bf 576} (2019), 142--157, DOI 10.1016/j.laa.2018.03.035, \url{https://doi.org/10.1016/j.laa.2018.03.035}.

@@

Morales, Alejandro H. and Yip, Martha, {\em The volume of the caracol polytope}, S\'{e}m. Lothar. Combin. {\bf 80B} (2018), Art. 87, 12.

@@

Morales, Alejandro H. and Yip, Martha, {\em A combinatorial model for computing volumes of flow polytopes}, Trans. Amer. Math. Soc. {\bf 372} (2019), 3369--3404, DOI 10.1090/tran/7743, \url{https://doi.org/10.1090/tran/7743}.
\item Bera, Sayani and Verma, Kaushal, {\em Some aspects of shift-like automorphisms of {$\Bbb C^k$}}, Proc. Indian Acad. Sci. Math. Sci. {\bf 128} (2018), Art. 10, 48, DOI 10.1007/s12044-018-0388-1, \url{https://doi.org/10.1007/s12044-018-0388-1}.

@@

{R}iemann surface}, Doc. Math. {\bf 23} (2018), 1291--1311.

@@

sufficient kernels}, Complex Anal. Oper. Theory {\bf 13} (2019), 2069--2093, DOI 10.1007/s11785-017-0701-5, \url{https://doi.org/10.1007/s11785-017-0701-5}.

@@

selected areas of functional analysis and operator theory}, Indian J. Pure Appl. Math. {\bf 50} (2019), 599--617, DOI 10.1007/s13226-019-0345-4, \url{https://doi.org/10.1007/s13226-019-0345-4}.

@@

interpolation and extension}, J. Funct. Anal. {\bf 274} (2018), 504--524, DOI 10.1016/j.jfa.2017.09.013, \url{https://doi.org/10.1016/j.jfa.2017.09.013}.

@@

developing countries {\bf 275} (2019), 42--64.
\item Bhosle, Usha N., {\em Hitchin pairs on reducible curves}, Internat. J. Math. {\bf 29} (2018), 1850015, 49, DOI 10.1142/S0129167X18500155, \url{https://doi.org/10.1142/S0129167X18500155}.

@@

Pingali, Vamsi P., {\em Rational cuspidal curves on del-{P}ezzo surfaces}, J. Singul. {\bf 17} (2018), 91--107.

@@

logarithmic connections}, Doc. Math. {\bf 24} (2019), 2299--2337.

@@

astheno-{K}\"{a}hler manifolds}, \'{E}pijournal Geom. Alg\'{e}brique {\bf 2} (2018), Art. 6, 13.

@@

{FEM} for the {O}seen problem}, Comput. Methods Appl. Math. {\bf 19} (2019), 189--214, DOI 10.1515/cmam-2018-0020, \url{https://doi.org/10.1515/cmam-2018-0020}.

@@

{${S}_n$}-invariant kernels}, J. Funct. Anal. {\bf 276} (2019), 751--784, DOI 10.1016/j.jfa.2018.10.025, \url{https://doi.org/10.1016/j.jfa.2018.10.025}.

@@

for some fractional {L}aplacians}, Commun. Pure Appl. Anal. {\bf 18} (2019), 2575--2605, DOI 10.3934/cpaa.2019116, \url{https://doi.org/10.3934/cpaa.2019116}.
\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal, {\em Comments on the {G}reen's function of a planar domain}, Anal. Math. Phys. {\bf 8} (2018), 383--414, DOI 10.1007/s13324-017-0177-5, \url{https://doi.org/10.1007/s13324-017-0177-5}.

@@

constraints}, ESAIM Control Optim. Calc. Var. {\bf 24} (2018), 1181--1206, DOI 10.1051/cocv/2017031, \url{https://doi.org/10.1051/cocv/2017031}.

@@

of manifolds}, Exp. Math. {\bf 27} (2018), 22--36, DOI 10.1080/10586458.2016.1212747, \url{https://doi.org/10.1080/10586458.2016.1212747}.

@@

indefinite second-order linear elliptic problems}, Comput. Methods Appl. Math. {\bf 19} (2019), 233--250, DOI 10.1515/cmam-2019-0034, \url{https://doi.org/10.1515/cmam-2019-0034}.

@@

the polydisc}, Complex Var. Elliptic Equ. {\bf 63} (2018), 1341--1352, DOI 10.1080/17476933.2017.1370461, \url{https://doi.org/10.1080/17476933.2017.1370461}.

@@

difference equation}, Discrete Contin. Dyn. Syst. {\bf 38} (2018), 1707--1718, DOI 10.3934/dcds.2018070, \url{https://doi.org/10.3934/dcds.2018070}.

@@

semipositive matrices}, Electron. J. Linear Algebra {\bf 34} (2018), 687--694, DOI 10.13001/1081-3810.3864, \url{https://doi.org/10.13001/1081-3810.3864}.

@@

{D}unkl-{H}ermite operator}, Proc. Edinb. Math. Soc. (2) {\bf 61} (2018), 513--544, DOI 10.1017/s0013091517000311, \url{https://doi.org/10.1017/s0013091517000311}.

@@

{K}lingen type {E}isenstein series and applications}, Abh. Math. Semin. Univ. Hambg. {\bf 89} (2019), 105--116, DOI 10.1007/s12188-019-00206-7, \url{https://doi.org/10.1007/s12188-019-00206-7}.
\item Das, Soumya and Khan, Rizwanur, {\em The third moment of symmetric square {$L$}-functions}, Q. J. Math. {\bf 69} (2018), 1063--1087, DOI 10.1093/qmath/hay012, \url{https://doi.org/10.1093/qmath/hay012}.

@@

2 in prime powers}, Acta Arith. {\bf 183} (2018), 167--172, DOI 10.4064/aa170419-4-11, \url{https://doi.org/10.4064/aa170419-4-11}.
\item Das, Soumya and Pal, Ritwik, {\em The first negative eigenvalue of {Y}oshida lifts}, Res. Number Theory {\bf 5} (2019), Paper No. 20, 9, DOI 10.1007/s40993-019-0158-x, \url{https://doi.org/10.1007/s40993-019-0158-x}.

@@

{A}rchimedean}, Discrete Math. {\bf 341} (2018), 3296--3309, DOI 10.1016/j.disc.2018.08.016, \url{https://doi.org/10.1016/j.disc.2018.08.016}.

@@

for convection-diffusion-reaction problems}, Numer. Methods Partial Differential Equations {\bf 35} (2019), 638--663, DOI 10.1002/num.22317, \url{https://doi.org/10.1002/num.22317}.

@@

the optimal control problems governed by {S}tokes equation}, Numer. Funct. Anal. Optim. {\bf 40} (2019), 421--460, DOI 10.1080/01630563.2018.1538158, \url{https://doi.org/10.1080/01630563.2018.1538158}.
\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P. and Silberman, Lior and Tao, Terence, {\em Homogeneous length functions on groups}, Algebra Number Theory {\bf 12} (2018), 1773--1786, DOI 10.2140/ant.2018.12.1773, \url{https://doi.org/10.2140/ant.2018.12.1773}.

@@

posteriori} error control of the obstacle problem}, Comput. Math. Appl. {\bf 75} (2018), 2311--2327, DOI 10.1016/j.camwa.2017.12.010, \url{https://doi.org/10.1016/j.camwa.2017.12.010}.

@@

3{D}-elliptic obstacle problem}, Comput. Methods Appl. Math. {\bf 18} (2018), 223--236, DOI 10.1515/cmam-2017-0018, \url{https://doi.org/10.1515/cmam-2017-0018}.
\item Garani, Shayan Srinivasa and Seshadri, Harish, {\em An algorithmic approach to {S}outh {I}ndian classical music}, J. Math. Music {\bf 13} (2019), 107--134, DOI 10.1080/17459737.2019.1604845, \url{https://doi.org/10.1080/17459737.2019.1604845}.
\item Gaussier, Herv\'{e} and Seshadri, Harish, {\em Holomorphic motions and complex geometry}, Proc. Amer. Math. Soc. {\bf 147} (2019), 301--313, DOI 10.1090/proc/14217, \url{https://doi.org/10.1090/proc/14217}.

@@

C^n$}}, Comput. Methods Funct. Theory {\bf 18} (2018), 617--641, DOI 10.1007/s40315-018-0243-5, \url{https://doi.org/10.1007/s40315-018-0243-5}.
\item Ghara, Soumitra and Kumar, Surjit, {\em On the sum of two subnormal kernels}, J. Math. Anal. Appl. {\bf 469} (2019), 1015--1027, DOI 10.1016/j.jmaa.2018.09.048, \url{https://doi.org/10.1016/j.jmaa.2018.09.048}.

@@

diffusions}, Stoch. Anal. Appl. {\bf 36} (2018), 1--27, DOI 10.1080/07362994.2017.1356732, \url{https://doi.org/10.1080/07362994.2017.1356732}.

@@

obstacle problem}, J. Comput. Appl. Math. {\bf 357} (2019), 85--102, DOI 10.1016/j.cam.2019.02.026, \url{https://doi.org/10.1016/j.cam.2019.02.026}.

@@

solving parabolic obstacle problem}, Comput. Math. Appl. {\bf 78} (2019), 3896--3915, DOI 10.1016/j.camwa.2019.06.022, \url{https://doi.org/10.1016/j.camwa.2019.06.022}.

@@

multishifts}, Proc. Amer. Math. Soc. {\bf 147} (2019), 2599--2608, DOI 10.1090/proc/14410, \url{https://doi.org/10.1090/proc/14410}.
